Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization.

### 2018-10-28 tex/paper.tex
Moved text to supplementary

The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% \fixme{Eide ? } of the brain volume 
and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.

@@

\subsection{MRI Data}
\begin{figure}
\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$.\fixme{copyright issues}. \lars{Reconstructed based on data obtained from \cite{eidevalnes}. eller fjerne upper row? } }
\label{fig1} 
\end{figure}

@@

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}). This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
\caption{The left panel show the anatomical map. The middle panel show the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Fig.\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices. 
%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.

@@

The results are given in Table~\ref{TAB::timesteps}. It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps. This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters. Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}. In Figure \ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time. These oscillations are caused by the value selection of $\alpha$, which tries minimize $g$ between observation times.

@@

The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}. In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps. This behavior is neither visible in Tab.\ref{TAB::timesteps} or in  Tab.\ref{TAB::double} for the same regularization parameters. The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}. Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.

@@

\subsubsection{The noise susceptibility}
The MRI data contains noise, hence an investigation to the noise susceptibility is needed. This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations. Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$. Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
of noise shown in the upper rows.

In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}. Then in Table~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect. The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$. Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.

@@

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation. The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$. The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 \mathrm{h}$ and $dt = 1 \mathrm{h}$.

The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}. From Table~\ref{Tab::Real-data},it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$. It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.

@@

The oscillation in Fig.\ref{boundarycontrol} showed a large discrepancy in the states between observations. Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}. It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters. Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$. Excluding the values with $\alpha=1.0\mathrm{e}{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter. Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$. This gives a difference of 42\% in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.

@@

In Fig.\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa. The regions with above average amount of tracers corresponds with high diffusivity regions in Figure~\ref{figuredti}. This suggests that the computed diffusion coefficients corresponds to these values. The ADC value in the high diffusivity regions are approximately  $1.4\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$. This gives a difference of $ 46 \%$ compared to the computed values.

@@

In Table~\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$. This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.

@@

\begin{table}
\centering
\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters. The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||^{rel}$ \\
\hline 
 1.0e+00 	 & 1.0e+02 	 & 10 & 437 	 & +4.631 & +0.283 & +0.103 & +0.127 \\ 
 1.0e+00 	 & 1.0e+00 	 & 10 & 129 	 & +1.638 & +0.224 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 129 	 & +1.602 & +0.223 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 151 	 & +1.608 & +0.223 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\ 
 \hline
 1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
 1.0e-02 	 & 1.0e+00 	 & 10 & 125 	 & -0.027 & +0.041 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 133 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 108 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
 \hline
 1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 143 	 & -0.036 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 108 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 158 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 \hline
 1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 117 	 & -0.035 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 120 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 122 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\

@@

@@

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel} $\\
\hline
 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & -0.030 & +0.041 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 120 	 & -0.032 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 125 	 & -0.038 & +0.039 & +0.037 & +0.026 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 167 	 & -0.040 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & -0.038 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 95 	 & -0.047 & +0.036 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 75 	 & -0.041 & +0.036 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 136 	 & -0.044 & +0.036 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 134 	 & -0.034 & +0.037 & +0.037 & +0.026 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 112 	 & -0.046 & +0.038 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 111 	 & -0.043 & +0.036 & +0.037 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 214 	 & -0.049 & +0.037 & +0.036 & +0.026 \\

>>>>

The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.

@@

\subsection{MRI Data}
\begin{figure}
\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
\label{fig1} 
\end{figure}

@@

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}. This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
\caption{The left panel show the anatomical map. The middle panel show the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices. 
%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.

@@

In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time. These oscillations are caused by the value selection of $\alpha$, which tries minimize $g$ between observation times.

@@

@@

\subsubsection{The noise susceptibility}
The MRI data contains noise, hence an investigation to the noise susceptibility is needed. This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations. Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$. Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
of noise shown in the upper rows.      
In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect. The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$. Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.

@@

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation. The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$. The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 \mathrm{h}$ and $dt = 1 \mathrm{h}$.

The results are shown in Table~\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}. From Table~\ref{Tab::Real-data}, it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$. It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.

@@

The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations. Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}. It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters. Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$. Excluding the values with $\alpha=1.0\mathrm{e}{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter. Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$. This gives a difference of 42\% in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.

@@

In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa. The regions with above average amount of tracers corresponds with high diffusivity regions in Figure~\ref{figuredti}. This suggests that the computed diffusion coefficients corresponds to these values. The ADC value in the high diffusivity regions are approximately  $1.4\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$. This gives a difference of $ 46 \%$ compared to the computed values.

@@

In Table~\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$. This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise}, where the noise is present at the boundary.

@@

\begin{table}
\centering
\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters. The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$.}
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||^{rel}$ \\
\hline 
 1.0e+00 	 & 1.0e+02 	 & 10 & 437 	 & +4.631 & +0.283 & +0.103 & +0.127 \\ 
 1.0e+00 	 & 1.0e+00 	 & 10 & 129 	 & +1.638 & +0.224 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 129 	 & +1.602 & +0.223 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 151 	 & +1.608 & +0.223 & +0.089 & +0.119 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\

 1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
 1.0e-02 	 & 1.0e+00 	 & 10 & 125 	 & -0.027 & +0.041 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 133 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 108 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\

 1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 143 	 & -0.036 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 108 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 158 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\

 1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 117 	 & -0.035 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 120 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 122 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\

@@

The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}. In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps. This behavior is neither visible in Table~\ref{TAB::timesteps} or in  Table~\ref{TAB::double} for the same regularization parameters. The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}. Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.

@@

In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel} $\\
\hline
 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & -0.030 & +0.041 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 120 	 & -0.032 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 125 	 & -0.038 & +0.039 & +0.037 & +0.026 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 167 	 & -0.040 & +0.039 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & -0.038 & +0.039 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 95 	 & -0.047 & +0.036 & +0.036 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 75 	 & -0.041 & +0.036 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 136 	 & -0.044 & +0.036 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 134 	 & -0.034 & +0.037 & +0.037 & +0.026 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 112 	 & -0.046 & +0.038 & +0.036 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 111 	 & -0.043 & +0.036 & +0.037 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 214 	 & -0.049 & +0.037 & +0.036 & +0.026 \\
